%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations/Posters}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvpubs}
\cvpub{\textbf{Jansen, D.}, Archie , E.A.2022. Can we replace assigned ranks by elo-based ranks?, Joint lab meeting, Duke, USA}

\cvpub{\textbf{Jansen, D.}, Archie , E.A. 2020. Do baboon dads matter?, Joint lab meeting, Duke, USA}

\cvpub{\textbf{Jansen, D.}, Archie , E.A. 2019. Issues with SCI and DSI and the possible solution of universal slopes. Joint lab meeting, Duke, USA}

\cvpub{\textbf{Jansen, D.}, Archie , E.A. 2018. Early adversity, social connectedness, and submission indexes for juveniles. Joint lab meeting, Duke, USA}

\cvpub{\textbf{Jansen, D.}, Archie , E.A. 2015. Condition data analysis. Joint lab meeting, Duke, USA}

\cvpub{\textbf{Jansen. D.} Cant, M.A., Manser, M.B. 2013. Context-specific call sequences in the banded mongoose. (poster) ABS conference. Boulder, USA}
   
   \cvpub{\textbf{Jansen. D.}, Cant, M.A.,  Manser, M.B. 2012. Temporal segregation of individual and behavioural signatures in banded mongoose (Mungos mungo) close calls. VIth ECBB. Essen, Germany}
   
\cvpub{\textbf{Jansen. D.} 2012. Complexity of information coding in banded mongoose vocalisations. EvoBio PhD retreat. Riederalp, Switerland}
\cvpub{\textbf{Jansen. D.} Cant, M.B.,  Manser, M.B. 2012. Close call transmission - a comparison between banded mongoose and meerkats. 4th annual Meerkat and Mongoose Meeting. Cambridge, UK}

\cvpub{\textbf{Jansen. D.} Cant, M.B.,  Manser, M.B. 2012. Temporal segregation of individual and behavioural signatures in banded mongoose close calls. . ASAB Easter meeting. Aberystwyth, UK}

\cvpub{\textbf{Jansen. D.} Cant, M.B.,  Manser, M.B.2012. Banded mongoose close calls encode individual- and behaviour-specific signatures. Biology 2012. Friborg, Switzerland}

\cvpub{\textbf{Jansen. D.} Cant, M.B.,  Manser, M.B. 2011. Banded mongoose close calls encode individual- and behaviour-specific signatures. . XXIII IBAC. La Rochelle, France}

\cvpub{\textbf{Jansen. D.}. 2011. Cooperation. Conflict and Communication in Banded Mongoose. Tropical Biology Association course. Mweya, Uganda}

\cvpub{\textbf{Jansen. D.} . 2010. Cooperation. Conflict and Communication in Banded Mongoose. Tropical Biology Association course. Mweya. Uganda}

\cvpub{\textbf{Jansen. D.}. 2009. Vocalizations of banded mongoose. UWA research symposium. Mweya, Uganda}

\cvpub{\textbf{Jansen. D.}. 2009. Banded mongoose research in Queen Elisabeth National Park. Tropical Biology Association course. Mweya, Uganda}

\cvpub{\textbf{Jansen. D.}. 2008. ‘Dinner time’. - resource calls in banded mongoose. . Institute of Zoology PhD retreat. Zurich,Switzerland}

\end{cvpubs}
