%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\begin{cvpubs}
    \cvpub{\textbf{Jansen, D.}, Langevelde, F., Boer, W. F. 2007. Optimization or satiation, testing diet selection rules in goats. Small Ruminant Research 73.1, pp. 160–168}
    
    \cvpub{\textbf{Jansen, D.}, Cant, M. A., Manser, M. B. 2012. Segmental concatenation of individual signatures and context cues in banded mongoose (Mungos mungo) close calls. BMC biology 10.1, pp. 1–11.}
    
    \cvpub{\textbf{Jansen, D.}, Cant, M. A., Manser, M. B. 2013. Testing for vocal individual discrimination in adult banded mongooses. Journal of Zoology 291.3, pp. 171–177.}
    
    \cvpub{\textbf{Jansen, D.} 2013 Vocal communication in banded mongoose. PhD thesis. Doctoral dissertation, University of Zürich.}

    \cvpub{Manser, M. B., \textbf{Jansen, D.}, Graw, B., Hollén, L. I., Bousquet, C. A., Furrer, R. D., Roux, A., 2014. Vocal complexity in meerkats and other mongoose species”. Advances in the Study of Behavior. Vol. 46. pp. 281–310.}

    \cvpub{Townsend, S. W., Koski, S. E., Byrne, R. W., Slocombe, K. E., Bickel, B., Boeckle, M., Braga Goncalves, I., Burkart, J. M., Flower, T., Gaunet, F., Glock, H., Gruber, T., \textbf{Jansen, D.}, Liebal, K., Linke, A., Miklósi, A., Moore, R., Schaik, C., Stoll, S., Vail, A., Waller, B., Wild, M., Zuberbühler, K., Manser, M. B., 2017. Exorcising G rice’s ghost: an empirical approach to studying intentional communication in animals. Biological Reviews 92.3, pp. 1427–1433.}

    \cvpub{Akinyi, M. Y.,\textbf{Jansen, D.}, Habig, B., Gesquiere, L. R., Alberts, S. C., Archie, E. A. 2019. Costs and drivers of helminth parasite infection in wild female baboons”. Journal of Animal Ecology 88, pp. 1029–1043.}

    \cvpub{Habig, B.,\textbf{Jansen, D.}, Akinyi, M. Y., Gesquiere, L. R., Alberts, S. C., Archie, E. A., 2019. Multi-scale predictors of parasite risk in wild male savanna baboons (Papio cynocephalus)”. Behavioral Ecology and Sociobiology 73.10, pp. 1–16.}

    \cvpub{
Levy, E. J., Zipple, M. N., McLean, E., Campos, F. A., Dasari, M., Fogel, A. S., Franz, M., Gesquiere, L. R., Gordon, J. B., Grieneisen, L., Habig, B.,\textbf{Jansen, D.}, Learn, C., Altmann, S., Archiel, E., 2020. A comparison of dominance rank metrics reveals multiple competitive
landscapes in an animal society. Proceedings of the Royal Society B 287.1934, p. 20201013.}

\cvpub{Grieneisen, L., Dasari, M., Gould, T. J., Björk, J. R., Grenier, J.C., Yotova, V.,\textbf{Jansen, D.}, Gottel, N., Gordon, J. B., Learn, N. H., 2021. Gut microbiome heritability is nearly universal but environmentally contingent”. Science 373.6551, pp. 181–186.}

\cvpub{Björk, J. R., Dasari, M. R., Roche, K., Grieneisen, L., Gould, T. J., Grenier, J.C., Yotova, V., Gottel, N.,\textbf{Jansen, D.}, Gesquiere, L. R., 2022. Synchrony and idiosyncrasy in the gut microbiome of wild baboons. Nature Ecology \& Evolution, pp. 1–10.}

\cvpub{Paietta, E. N., Weibel, C. J.,\textbf{Jansen, D.}, Mututua, R. S., Warutere, J. K., Siodi, I. L., Gesquiere, L. R., Obanda, V., Alberts, S. C., Archie, E. A. 2022. Troubled waters: Water availability drives human-baboon encounters in a protected, semi-arid landscape. Biological Conservation 274, p. 109740.}

\cvpub{Gordon, J.\textsc{*},  \textbf{Jansen, D.},\textsc{*} , Learn, N., Archie, E., Tung, J., Altmann, J., Alberts, S.C. 2022. Ordinal dominance rank assignments: Matrix-based versus Elo-based. Technical report; Duke university. (\textsc{*} shared first authorship)}

\cvpub{Björk J.R., Dasari M., Grieneisen L., \textbf{Jansen D.}, Gould T.J., Gesquiere L.R., Barreiro L.B., Alberts S.C., Blekhman R., Gilbert J.A., Tung J., Mukherjee, S., Archie E.A.  2023. Universal gut microbial relationships in the gut microbiome of wild baboons. eLife. 12:e83152}
    
\small \color{black}
    \cvpub{\textbf{Jansen, D.}, Alberts, S. C., Archie, E. A., (in prep).  Grooming interactions with fathers increase adult female survival}

\end{cvpubs}

% %---------------------------------------------------------
